---
title: "MislabelProbs"
author: "Christine Stawitz"
date: "January 29, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Calculating consumption probabilities

We use logistic regression to estimate the probability a seafood item is consumed on a given day $y$, $p_{cons,y}$ from NHANES data.
$$log\left(\frac{p_{cons,y}}{1-p_{cons,y}}\right)=\beta_0+\sum_i \beta_ix_i + \beta_wI_w+\beta_sI_s$$
Where $\beta_i$ are the coefficients on explanatory variables $x_i$. The explanatory variables include gender (riagendr), age at screening in years (ridageyr), race/ethicity (ridreth1), and ratio of family income to poverty (indfmpir).

```{r dataanalysis,warning=FALSE}
load("./data/NHANES_all.RData")
#Check correlations
M <- cor(dat[,c("indfmpir","riagendr","ridageyr","ridreth1", "indhhin2")], use="pairwise.complete.obs")

corrplot::corrplot(M,method="circle")
dat$ridreth1 <- factor(dat$ridreth1, levels=c("3","1","2","4","5"))
dat$riagendr <- factor(dat$riagendr)
dat$ateSalmon <- ifelse(dat$drd370mq>0,dat$drd370mq/30,0)
dat$ateSalmon[is.na(dat$ateSalmon)]<-0
dat$any_seafood[is.na(dat$any_seafood)]<-0
require(survey)
full_salmon <- svyglm(ateSalmon~indfmpir+riagendr+ridageyr+ridreth1,family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))
summary(full_salmon)
drop1(full_salmon)

#require(lme4)
#full.glmer <- glmer(ateSalmon~indfmpir+riagendr+ridageyr+ridreth1,family=quasibinomial(link="logit"), data=dat)


dat$ateTuna <- ifelse(dat$drd370bq>0,dat$drd370bq/30,0)
dat$ateTuna[is.na(dat$ateTuna)]<-0
full_tuna <- svyglm(ateTuna~indfmpir+riagendr+ridageyr+ridreth1,family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))
summary(full_tuna)
drop1(full_tuna)

dat$ateCod <- ifelse(dat$drd370eq>0,dat$drd370eq/30,0)
dat$ateCod[is.na(dat$ateCod)]<-0
full_cod <- svyglm(ateCod~indfmpir+riagendr+ridageyr+ridreth1,family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=quasibinomial(link="logit"), data=dat)

summary(full_cod)
drop1(full_cod)


dat$ateCrab <- ifelse(dat$drd350bq>0,dat$drd350bq/30,0)
dat$ateCrab[is.na(dat$ateCrab)]<-0
full_crab <- svyglm(ateCrab~indfmpir+riagendr+ridageyr+ridreth1,family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=quasibinomial(link="logit"), data=dat)

summary(full_crab)
drop1(full_crab)

dat$ateShrimp <- ifelse(dat$drd350hq>0,dat$drd350hq/30,0)
dat$ateShrimp[is.na(dat$ateShrimp)]<-0
full_Shrimp <- svyglm(ateShrimp~indfmpir+riagendr+ridageyr+ridreth1,family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

best_Shrimp <- svyglm(ateShrimp~indfmpir+ridageyr+ridreth1, family=quasibinomial(link="logit"), design = svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=quasibinomial(link="logit"), data=dat)

summary(full_Shrimp)
drop1(full_Shrimp)


dat$ateScal <- ifelse(dat$drd350gq>0,dat$drd350gq/30,0)
dat$ateScal[is.na(dat$ateScal)]<-0
full_Scal <- svyglm(ateScal~indfmpir+riagendr+ridageyr+ridreth1,family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

best_Scal <- svyglm(ateScal~indfmpir+ridageyr+ridreth1, family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=quasibinomial(link="logit"), data=dat)

summary(best_Scal)
drop1(full_Scal)


dat$ateOy <- ifelse(dat$drd350fq>0,dat$drd350fq/30,0)
dat$ateOy[is.na(dat$ateOy)]<-0
full_oy <- svyglm(ateOy~indfmpir+riagendr+ridageyr+ridreth1,family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))
best_oy <- svyglm(ateOy~indfmpir+ridreth1,family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))
#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=quasibinomial(link="logit"), data=dat)

summary(best_oy)
drop1(full_oy)

dat$ateClam <- ifelse(dat$drd350aq>0,dat$drd350aq/30,0)
dat$ateClam[is.na(dat$ateClam)]<-0
full_clam <- svyglm(ateCod~indfmpir+riagendr+ridageyr+ridreth1,family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=quasibinomial(link="logit"), data=dat)

summary(full_clam)
drop1(full_clam)

dat$ateLob <- ifelse(dat$drd350dq>0,dat$drd350dq/30,0)
dat$ateLob[is.na(dat$ateLob)]<-0
full_lob <- svyglm(ateLob~indfmpir+riagendr+ridageyr+ridreth1,family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

best_lob <- svyglm(ateLob~indfmpir+ridageyr+ridreth1,family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=quasibinomial(link="logit"), data=dat)

summary(best_lob)
drop1(full_lob)


dat$ateCatf <- ifelse(dat$drd370dq>0,dat$drd370dq/30,0)
dat$ateCatf[is.na(dat$ateCatf)]<-0
best_catf <- svyglm(ateCatf~ridageyr+ridreth1,family=quasibinomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=quasibinomial(link="logit"), data=dat)

summary(best_catf)
```


## High level summary

Excluding catfish, where income was not a significant predictor of consumption, higher income correlated with more seafood consumption. Across all seafood types, older people were more likely to consume seafood. Women were more likely to eat salmon, tuna, crab. Men were more likely to eat 
oysters and catfish. Gender was not a significant predictor of consumption probability for other seafood types. All racial and ethnic categories had significantly different seafood consumption than whites. 

## Predicted seafood consumption
```{r}

#From models
pop <- data.frame(indfmpir=mean(dat$indfmpir, na.rm=T), riagendr=factor(2), ridageyr=mean(dat$ridageyr, na.rm=T),ridreth1=factor(3))
meanWF <- predict(full_salmon, newdata=pop, type="response")
pop <- data.frame(indfmpir=mean(dat$indfmpir, na.rm=T), riagendr=factor(1), ridageyr=mean(dat$ridageyr, na.rm=T),ridreth1=factor(3))

meanWM <- predict(full_salmon, newdata=pop, type="response")

#Simple means
desobject <- svydesign(id=~seqn, weights=~wtmec8yr,
                       data=dat)

getP <- function(column.name){
  newcol <-  ifelse(column.name>0,column.name/30,0)
  newcol[is.na(newcol)]<-0
  return(newcol)
}

#There's some way to do this better with dplyr but it's taking me too long to figure out!
dat$ateTuna <-getP(dat$drd370bq)
dat$ateSalmon <- getP(dat$drd370mq)
dat$ateCod <- getP(dat$drd370eq)
dat$ateCrab <- getP(dat$drd350bq)
dat$ateShrimp <- getP(dat$drd350hq)
dat$ateScal <-getP(dat$drd350gq)
dat$ateOy <- getP(dat$drd350fq)
dat$ateClam <- getP(dat$drd350aq)
dat$ateLob <- getP(dat$drd350dq)
dat$ateCatf <- getP(dat$drd370dq)

probs <- list("salmon"=svymean(~ateSalmon, design = desobject, data=dat),
               "tuna"=svymean(~ateTuna, design = desobject),
"cod"=svymean(~ateCod, design = desobject),
"crab"=svymean(~ateCrab, design = desobject),
"shrimp"=svymean(~ateCrab, design = desobject),
"scallop"=svymean(~ateCrab, design = desobject),
"Oyster"=svymean(~ateCrab, design = desobject),
"clam"=svymean(~ateCrab, design = desobject),
"lobster"=svymean(~ateCrab, design = desobject),
"catfish"=svymean(~ateCrab, design = desobject))
(probs)

```




