---
title: "MislabelProbs"
author: "Christine Stawitz"
date: "January 29, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Calculating consumption probabilities

We use logistic regression to estimate the probability a seafood item is consumed on a given day $y$, $p_{cons,y}$ from NHANES data.
$$log\left(\frac{p_{cons,y}}{1-p_{cons,y}}\right)=\beta_0+\sum_i \beta_ix_i + \beta_wI_w+\beta_sI_s$$
Where $\beta_i$ are the coefficients on explanatory variables $x_i$. The explanatory variables include gender (riagendr), age at screening in years (ridageyr), race/ethicity (ridreth1), and ratio of family income to poverty (indfmpir).

```{r data load}
load("./data/NHANES_all.RData")
#Check correlations
M <- cor(dat[,c("indfmpir","riagendr","ridageyr","ridreth1", "indhhin2")], use="pairwise.complete.obs")

corrplot::corrplot(M,method="circle")
dat$ridreth1 <- factor(dat$ridreth1)
dat$ateSalmon <- ifelse(dat$drd370mq>0,1,0)
dat$ateSalmon[is.na(dat$ateSalmon)]<-rep(0,length(is.na(dat$ateSalmon)))
dat$any_seafood[is.na(dat$any_seafood)]<-rep(0,length(is.na(dat$any_seafood)))
require(survey)
full_salmon <- svyglm(ateSalmon~indfmpir+riagendr+ridageyr+ridreth1,family=binomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))
drop1(full_salmon)
#require(lme4)
#full.glmer <- glmer(ateSalmon~indfmpir+riagendr+ridageyr+ridreth1,family=binomial(link="logit"), data=dat)


dat$ateTuna <- ifelse(dat$drd370bq>0,1,0)
dat$ateTuna[is.na(dat$ateTuna)]<-0
full_tuna <- svyglm(ateTuna~indfmpir+riagendr+ridageyr+ridreth1,family=binomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))
summary(full_tuna)
drop1(full_tuna)

dat$ateCod <- ifelse(dat$drd370eq>0,1,0)
dat$ateCod[is.na(dat$ateCod)]<-0
full_cod <- svyglm(ateCod~indfmpir+riagendr+ridageyr+ridreth1,family=binomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=binomial(link="logit"), data=dat)

summary(full_cod)
drop1(full_cod)


dat$ateCrab <- ifelse(dat$drd350bq>0,1,0)
dat$ateCrab[is.na(dat$ateCrab)]<-0
full_crab <- svyglm(ateCrab~indfmpir+riagendr+ridageyr+ridreth1,family=binomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=binomial(link="logit"), data=dat)

summary(full_crab)
drop1(full_crab)

dat$ateShrimp <- ifelse(dat$drd350hq>0,1,0)
dat$ateShrimp[is.na(dat$ateShrimp)]<-0
full_Shrimp <- svyglm(ateShrimp~indfmpir+riagendr+ridageyr+ridreth1,family=binomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=binomial(link="logit"), data=dat)

summary(full_Shrimp)
drop1(full_Shrimp)


dat$ateScal <- ifelse(dat$drd350gq>0,1,0)
dat$ateScal[is.na(dat$ateScal)]<-0
full_Scal <- svyglm(ateScal~indfmpir+riagendr+ridageyr+ridreth1,family=binomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=binomial(link="logit"), data=dat)

summary(full_Scal)
drop1(full_Scal)

dat$ateOy <- ifelse(dat$drd350fq>0,1,0)
dat$ateOy[is.na(dat$ateCod)]<-0
full_oy <- svyglm(ateOy~indfmpir+riagendr+ridageyr+ridreth1,family=binomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=binomial(link="logit"), data=dat)

summary(full_oy)
drop1(full_oy)


dat$ateClam <- ifelse(dat$drd350aq>0,1,0)
dat$ateClam[is.na(dat$ateClam)]<-0
full_clam <- svyglm(ateCod~indfmpir+riagendr+ridageyr+ridreth1,family=binomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=binomial(link="logit"), data=dat)

summary(full_clam)
drop1(full_clam)

dat$ateLob <- ifelse(dat$drd350dq>0,1,0)
dat$ateLob[is.na(dat$ateLob)]<-0
full_lob <- svyglm(ateLob~indfmpir+riagendr+ridageyr+ridreth1,family=binomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=binomial(link="logit"), data=dat)

summary(full_lob)
drop1(full_lob)


dat$ateCatf <- ifelse(dat$drd370dq>0,1,0)
dat$ateCatf[is.na(dat$ateCatf)]<-0
full_catf <- svyglm(ateCatf~indfmpir+riagendr+ridageyr+ridreth1,family=binomial(link="logit"), design=svydesign(ids=~1, weights=~wtmec8yr, data=dat))

#full_cod.r <- glmer(ateCod~indfmpir+riagendr+ridageyr+ridreth1+(1|year),family=binomial(link="logit"), data=dat)

summary(full_catf)
drop1(full_catf)
```


```{r}

```

